\documentclass[a4paper]{article}

\setcounter{section}{-1}

\begin{document}

\section{General Theory}
There is some fundamental magic particle (the name of this particle is not yet known, this is subject to the linguistics and history that will eventually be implemented in the worldbuilding). Every such particle that exists contributes in some amount to a field. Each point in the field has a strength value determined by its interactions with particles, and these values will determine the movement and stability of the particle. The lower the stability of the particle, the more likely it is over time to dissociate into pure energy, which will be transmuted to other types of energy based on quantized energy levels of the initial particle. The strength of the field will also determine the likelihood of spontaneous magic particle coalescence from surrounding energy.

There are forces that act on magic particles. Namely, they are affected by gravity, they are attracted to one another dependent on the measure of intrinsic energy they possess, and they are repelled from one another dependent on the measure of superficial energy they possess (each particle contains two types of energy, intrinsic and superficial. Intrinsic energy is at balance with the mass of a particle to together equal a universal constant, whereas superficial energy is unaffected by this and will change depending on the surroundings of the particle).

Magic particles will commonly unite to form bonded complexes. This is because intrinsic energy can have a non-uniform density around the surface of the particle, and the placement of energy nodes are subject to the same forces that affect the energy of entire particles, and can affect the particles' stability.

\end{document}
